Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
table fix
proofs

We imagine integrated activity diaries to be used by both clinicans
and patients in several ways.  First, for nearly all types of
conditions, monitoring a person's overall daily activity and sleep
duration can easily indicate how much rest, exercise, exposure to
others, and the outside world he or she might be getting.  Daily
records of the time(s) that a person gets up, eats, works, exercises
and relaxes can be analysed by clincians for irregular behaviours or
habits that might be affecting a person's well-being. For more
specific conditions, daily measurements of a person's blood pressure,
blood oxidation, heart rate, breathing, weight, and galvanic skin
response could be useful for tracking progress along an clinician
prescribed intervention, recovery from illness, or onset of new
conditions, be used to pinpoint sources of prolonged stress.

>>>>

We imagine integrated activity diaries to be used by both clinicans
and patients in several ways.  First, for nearly all types of
conditions, monitoring a person's overall daily activity and sleep
duration could easily indicate how much rest, exercise, exposure to
others, and the outside world he or she might be getting.  Daily
records of the time(s) that a person gets up, eats, works, exercises
and relaxes can be analysed by clincians for irregular behaviours or
habits that might be affecting a person's well-being. For more
specific conditions, daily measurements of a person's blood pressure,
blood oxidation, heart rate, breathing, weight, and galvanic skin
response could be useful for tracking progress on a prescribed
intervention, recovery from an illness, or onset of a new conditions,
for example, or be used to pinpoint sources of prolonged stress.
